---
title: "Week 9 Data Story Submission"
author: "Esther Kho Yining"
date: "2024-03-19"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Week 9 

### What is the topic that you have finalized? (Answer in 1 or 2 sentences)
The topic that I have finalized is about the correlation between the popularity of Spotify songs and the elements of the music. 

### What are the data sources that you have curated so far? (Answer 1 or 2 sentences).
The data source I have obtained is for free, and originates from the following link: https://www.kaggle.com/datasets/sujaykapadnis/spotify-songs 

The data set contains information on the track popularity, danceability of the music, energy of the music and liveliness of the music.

```{r,eval=TRUE,echo=TRUE}
# Data set
library(tidyverse)
Spotify <- read.csv("spotify_songs.csv")

# First 5 rows of the data set
head(Spotify, 5)
```

## Week 10

### What is the question that you are going to answer? 
Does the popularity of Spotify music and correlation to elements of the music suggest any insightful reflections on how people remember things?

### Why is this an important question? 

Despite not being able to recall the majority of events in their lives, Dr Timothy Byron and Dr Jadey O'Regan (2022) highlights that many individuals have the ability to remember a song, even if they have not heard it in a long time. This ability to remember a song may be attributed to the catchiness and the tempo of the song which allows the song to remain memorable and popular for a long time once learned. As the popularity of the song is dependent on how memoriable it is to individuals (Byron & O'Regan, 2022), understanding the elements of popular music reflects the essential components that help people to remember things.

### Which rows and columns of the dataset will be used to answer this question? 

I will use the columns: 
Track popularity, Playlist Genre, Danceability, Valence, Speechiness, Tempo,  

As of submitting this document, I intend to work with the first 50 row from each playlist genre as the data is ordered based on the 6 different playlist genre. 


\newpage 

&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;**References** 

Byron, T., & O’Regan, J. (2022). _Hooks in popular music_. NSW, Australia. 

&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;Springer Nature.